Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-01-05 Code/R/RMarkdown/EntropyPlots.Rmd
codes test

>>>>

```{r Table_test_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

load("./Data/results_gi0_1.Rdata")

# Interpretación de rechazo o no rechazo
for (mu_val in mu_values) {
  results_data <- results_gi0_1[[as.character(mu_val)]]

  table_result <- kbl(
    results_data,
   # caption = paste("Hypothesis Testing for $G_I^0$, $\\mu =", mu_val, "$, $L=2$, $\\pha1=-1000$ , #$H_{\\Gamma_{\\text{SAR}}}=2.493$."),
    format = "latex",
    booktabs = TRUE,
    align = "c",
    escape = FALSE,
    digits = 4,
    label = "table_hipotesis"
  ) %>%
    collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")

  cat("### Results for mu =", mu_val, "\n")
  print(table_result)

  # Interpretación de rechazo o no rechazo
  cat(ifelse(nrow(results_data) > 0,
             paste("For mu =", mu_val, ":\n"),
             paste("No observations for mu =", mu_val, ":\n")))

  cat(ifelse(nrow(results_data) > 0,
             paste(
               "Sample Size ", results_data$`$n$`, " Estimator ", results_data$Estimator,
               ifelse(results_data$RejectNull,
                      " the null hypothesis is rejected.",
                      " the null hypothesis is not rejected."
               ), "\n"
             ),
             "\n"))
}

### 2024-01-05 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
codes test

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
#library(RColorBrewer)
library(ggsci)
#library(wesanderson)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)

@@

source("../../../Code/R/MainFunctions/gamma_sar_sample.r")
source("../../../Code/R/MainFunctions/entropy_gamma_sar.r")
source("../../../Code/R/MainFunctions/entropy_gI0.r")
source("../../../Code/R/MainFunctions/gi0_sample.r")

source("../../../Code/R/MainFunctions/van_es_estimator.r")
source("../../../Code/R/MainFunctions/correa_estimator.r")
source("../../../Code/R/MainFunctions/ebrahimi_estimator.r")
source("../../../Code/R/MainFunctions/noughabi_arghami_estimator.r")
source("../../../Code/R/MainFunctions/vasicek_estimator.r")
source("../../../Code/R/MainFunctions/al_omari_1_estimator.r")
source("../../../Code/R/MainFunctions/al_omari_2_estimator.r")

source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.r")
source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.r")
source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.r")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../../../Code/R/Programs/functions_sample_bias_mse.R")#

@@

\textcolor{red}{Our aim is to develop a test statistic that helps discriminating between fully-developed speckle and heterogeneous clutter.
We work with non-parametric estimators of the entropy, we reduce the bias of those based on spacings using bootstrap, and select the best ones.
Next, we study the empirical distribution of these estimators under the null hypothesis, followed by a study of the size and power of the proposed test.
We conclude the study with applications to SAR data.}

@@

## Estimation of the Shannon Entropy

@@

# Hypothesis testing based on non-parametric entropy {#sec:test}
General asymptotic results for functions of spacings are detailed&nbsp;\cite{Khashimov1990}, while&nbsp;\cite{Bert1992} developed a correction for the case of Shannon entropy.
Following the work of these authors, the next result applies: 
\begin{lemma}
Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, holds that:
\begin{equation*}
\sqrt{n}\,\Big(\label{Eq:bias_t}
\widetilde{H}_{i}+\int_{-\infty}^\infty f(z)\ln f(z) \mathrm{d}z\Big)
\xrightarrow[]{\mathcal{D}}
\mathcal{N}(0,\operatorname{Var}(\ln f(Z))).
\end{equation*}
\end{lemma} 
Consider, starting from the previous lemma, the test of the null hypothesis $\mathcal{H}_0: T_{\mathcal{D}}=D_0$ as opposed to one of the other three:
\begin{align*}
\mathcal{H}_1 &: T_{\mathcal{D}}\neq D_0,\\ 
\mathcal{H}_1 &: T_{\mathcal{D}}> D_0,\text{ or}\\
\mathcal{H}_1 &: T_{\mathcal{D}}< D_0. 
\end{align*}
For this purpose, we can use the test statistics:
\begin{equation*}
Z_{m,n} = \frac{\sqrt{n}\big(\label{Eq:bias4}
\widetilde{H}-D_0\big)}{\sqrt{\operatorname{Var}\big(\ln f(Z)\big)}},
\end{equation*}
so the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cumulative distribution function, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.

The power function for case (i) (two-sided test) at $t\neq D_0$ is given by
\begin{multline*}
\pi_{m,n}(t)=1-\Phi_{m,n}\Big(z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big)\\+\Phi_{m,n}\Big(-z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big),
\end{multline*}
for a sequence of cumulative distribution functions $\Phi_{m,n}(x)$ which tends uniformly to $\Phi_{\mathcal N}(z)$.

@@

# Number of replications
R <- 10

@@

A hypothesis testing was conducted using non-parametric entropy estimators as test statistics. 
The results in Table&nbsp;\ref{tab:table_hipotesis} show that data from the $G_I^0$ distribution exhibit fully developed speckle behavior, specifically in the limit case with parameters $\mu=5$, $L=2$, and $\alpha= -1000$. 
The true entropy of $\Gamma_{\text{SAR}}$ was set at $H_{\Gamma_{\text{SAR}}} = 2.493$.  
It is observed that, for different sample sizes, entropy values converge towards the true value of the Gamma SAR distribution. 
Hypothesis test results were conducted with a \SI{95}{\percent} confidence level. 
The $Z$ statistic measures the discrepancy between the estimated entropy and the true entropy. 
The $p$-values associated with the $Z$ statistic are predominantly greater than $0.05$, for sample sizes above $25$, suggesting that the data are consistent with the null hypothesis.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
#library(wesanderson)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)

@@

if(!require("rstudioapi")) install("rstudioapi")
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
source("../../../Code/R/MainFunctions/entropy_gamma_sar.R")
source("../../../Code/R/MainFunctions/entropy_gI0.R")
source("../../../Code/R/MainFunctions/gi0_sample.R")

source("../../../Code/R/MainFunctions/van_es_estimator.R")
source("../../../Code/R/MainFunctions/correa_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
source("../../../Code/R/MainFunctions/noughabi_arghami_estimator.R")
source("../../../Code/R/MainFunctions/vasicek_estimator.R")
source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
source("../../../Code/R/MainFunctions/al_omari_2_estimator.R")

source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../../../Code/R/Programs/functions_sample_bias_mse.R")#

@@

Our aim is to develop a test statistic that helps discriminating between fully-developed speckle and heterogeneous clutter.
We work with non-parametric estimators of the entropy, we reduce the bias of those based on spacings using bootstrap, and select the best ones.
Next, we study the empirical distribution of these estimators under the null hypothesis, followed by a study of the size and power of the proposed test.
We conclude the study with applications to SAR data.

@@

In Fig.&nbsp;\ref{fig:Plot_GI0_to_gamma}, we depict the behavior of the entropy of \(G_I^0\) when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.

```{r Plot_GI0_to_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=5$."}

L <- c(5)
alphas <- c(  -3, -8, -20, -1000)
alpha_labels <- c( expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -20), expression(italic(alpha) == -1000))

# Entropy GI0

muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")

# Entropy Gamma SAR

entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))

Entropy_gamma <- data.frame(mu, entropies_gamma)

Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")

#plot

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "solid",linewidth = 1.5) + 
  geom_line(linetype = "longdash",  linewidth = 2, alpha=.7) +
  annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  scale_color_manual(values = brewer.pal(7, "Dark2")[1:5], labels = alpha_labels) +
  #scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")

The empirical distributions of $\Gamma_{\text{SAR}}$ and $G_I^0$ entropies are shown in Fig.&nbsp;\ref{fig:Plot_empirical}. It is observed that when $\alpha$ approaches negative infinity, the two distributions are very similar. In other words, the mean entropy of $G_I^0$ approximates the mean entropy of $\Gamma_{\text{SAR}}$.

```{r Plot_empirical, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=5$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}

set.seed(1234567890, kind = "Mersenne-Twister")

R <- 3000
mu <- 1
L <- 5
B <- 1
sample.size <- c( 121)

alpha1_values <- c(-3, -8, -20, -1000)

plots_list <- list()

for (alpha_val in alpha1_values) {

  alpha1 <- alpha_val

  TestStatistics1 <- NULL
  TestStatistics2 <- NULL

  mean_entropy1 <- numeric(length(sample.size))
  mean_entropy2 <- numeric(length(sample.size))

  for (s in sample.size) {
    TestStat1 <- numeric(R)
    TestStat2 <- numeric(R)

    for (r in 1:R) {
      z <- gi0_sample(mu, alpha1, L, s)
      TestStat1[r] <- log(mean(z))  + (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      TestStat2[r] <- log(mean(z))  + (L - log(L) + lgamma(L) +(1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1)) - (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))

      #TestStat1[r] <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
      #TestStat2[r] <- -bootstrap_correa_estimator_log_mean(z, B) - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L) + L + lgamma(L - alpha1) - (L - alpha1) * (digamma(L - alpha1)) + (1 - alpha1) * digamma(-alpha1) - log(-1 - alpha1) - lgamma(-alpha1))
    }

    # mean_entropy1[sample.size == s] <- mean(TestStat1)
    # #cat(" mean for TestStat1", mean_entropy1[sample.size == s], "\n")
    # 
    # mean_entropy2[sample.size == s] <- mean(TestStat2)
    # cat(" mean for TestStat2", mean_entropy2[sample.size == s], "\n")

    TestStatistics1 <- rbind(TestStatistics1, data.frame("Sample_Size" = rep(s, R), "Test_Statistics" = TestStat1))
    TestStatistics2 <- rbind(TestStatistics2, data.frame("Sample_Size2" = rep(s, R), "Test_Statistics2" = TestStat2))
  }

  max_density1 <- max(density(TestStatistics1$Test_Statistics)$y, na.rm = TRUE)
  max_density2 <- max(density(TestStatistics2$Test_Statistics2)$y, na.rm = TRUE)

  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    annotate("text", x = max(TestStatistics1$Test_Statistics) + 0.1, y = max_density1,
             label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 5, hjust = 5, color = "red") +
    annotate("text", x = max(TestStatistics2$Test_Statistics2) + 0.1, y = max_density2,
             label = TeX("$G_I^0$"), vjust = 5, hjust = 5, color = "blue") +
    labs(x = "Entropy", y = "Empirical Density") +
    annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )

  plots_list[[as.character(alpha_val)]] <- plot
}

grid.arrange(grobs = plots_list, ncol = 2)

```
## Estimation of the Shannon Entropy

@@

# Hypothesis testing based on non-parametric entropy {#sec:test}
General asymptotic results for functions of spacings are detailed&nbsp;\cite{Khashimov1990}, while&nbsp;\cite{Bert1992} developed a correction for the case of Shannon entropy.
Following the work of these authors, the next result applies: 
\begin{lemma}
Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, holds that:
\begin{equation*}
\sqrt{n}\,\Big(\label{Eq:bias_t}
\widetilde{H}_{i}+\int_{-\infty}^\infty f(z)\ln f(z) \mathrm{d}z\Big)
\xrightarrow[]{\mathcal{D}}
\mathcal{N}(0,\operatorname{Var}(\ln f(Z))).
\end{equation*}
\end{lemma} 
Consider, starting from the previous lemma, we aim at testing the following hypotheses:

$$
 \begin{cases}\mathcal{H}_0: \mathcal{D}(\bm{\theta})=\Gamma_{\text{SAR}} \\ 
  \mathcal{H}_1: \mathcal{D}(\bm{\theta})=G_I^0.\end{cases}
$$
In other words, we verify the hypothesis that the data are fully-developed speckle.
<!-- \begin{align*} -->
<!-- \mathcal{H}_1 &: T_{\mathcal{D}}\neq D_0,\\  -->
<!-- \mathcal{H}_1 &: T_{\mathcal{D}}> D_0,\text{ or}\\ -->
<!-- \mathcal{H}_1 &: T_{\mathcal{D}}< D_0.  -->
<!-- \end{align*} -->
For this purpose, we use the following test statistic:
\begin{equation}
\label{Eq:test_e}
S(Z)= \widetilde{H}(Z)-H(Z).
\end{equation}
This test statistic $S(Z)$ aims to assess the behavior of the data under the null hypothesis, through the empirical distribution of the test statistic values for a sample size of $n$. The density should center around zero if the test statistic is capable of detecting that the data are fully-developed speckle, i.e., $S(Z)\approx 0$. Otherwise, under the alternative hypothesis, the empirical distribution of the test statistic values is not centered around zero. This suggests significant differences and implies the presence of heterogeneous clutter.

<!-- so the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cumulative distribution function, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.   -->

@@

set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)
# Number of replications para simulacion montecarlo para calculo de error tipo 1

N <- 1000

# Number of replications para calcular las entropias
R <- 10

@@

Fig.&nbsp;\ref{fig:Plot_empirical_test} displays the empirical distributions using statistical test \eqref{Eq:test_e}. Under the null hypothesis, we observe that the densities are centered around zero. Conversely, under the alternative hypothesis, such as for $\alpha=8$, the density is not centered around zero. It reveals the difference between the entropy of Gamma SAR and $G_I^0$, indicating that we are in a scenario of heterogeneous clutter.

```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under null hypothesis (centered around zero) and alternative hypothesis (e.g., $\\alpha=8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}

set.seed(1234567890, kind = "Mersenne-Twister")

R <- 3000
mu <- 1
L <- 5
B <- 2
sample.size <- c( 81)

alpha1_values <- c( -8)

plots_list <- list()

for (alpha_val in alpha1_values) {

  alpha1 <- alpha_val

  TestStatistics1 <- NULL
  TestStatistics2 <- NULL

  mean_entropy1 <- numeric(length(sample.size))
  mean_entropy2 <- numeric(length(sample.size))

  for (s in sample.size) {
    TestStat1 <- numeric(R)
    TestStat2 <- numeric(R)

    for (r in 1:R) {
      z <- gi0_sample(mu, alpha1, L, s)
      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      TestStat2[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1))- (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))

    }

    mean_entropy1[sample.size == s] <- mean(TestStat1)
   # cat(" mean for TestStat1", mean_entropy1[sample.size == s], "\n")

    mean_entropy2[sample.size == s] <- mean(TestStat2)
   # cat(" mean for TestStat2", mean_entropy2[sample.size == s], "\n")

    TestStatistics1 <- rbind(TestStatistics1, data.frame("Sample_Size" = rep(s, R), "Test_Statistics" = TestStat1))
    TestStatistics2 <- rbind(TestStatistics2, data.frame("Sample_Size2" = rep(s, R), "Test_Statistics2" = TestStat2))
  }

  difference.betweeen.GammaSAR.GI0.n.Look <- function(alpha, L) {
    return(
      -L - lgamma(L-alpha) + 
        (L-alpha)*(digamma(L - alpha))- 
        (1-alpha)*digamma(- alpha)+
        log(-1 - alpha)+
        lgamma(-alpha)
    )
  }

  max_density1 <- max(density(TestStatistics1$Test_Statistics)$y, na.rm = TRUE)
  max_density2 <- max(density(TestStatistics2$Test_Statistics2)$y, na.rm = TRUE)

  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=7, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
   # geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-20, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
   # annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-20, 5), y=7, parse=TRUE, label="alpha==-20", hjust=-.1, vjust=2.0, col="darkgreen") +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    #annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), y=7, parse=TRUE, label="alpha==-1000", hjust=-.1, vjust=4.0, col="darkgreen") +
    labs(x = "Test Statistics", y = "Empirical Density") +
    #annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )

  plots_list[[as.character(alpha_val)]] <- plot
}

grid.arrange(grobs = plots_list, ncol = 1)

A hypothesis testing was conducted using non-parametric entropy estimators as test statistics. 
The results in Table&nbsp;\ref{tab:table_hipotesis} show that data from the $G_I^0$ distribution exhibit fully developed speckle behavior, specifically in the limit case with parameters $\mu=5$, $L=2$, and $\alpha= -1000$. 
The true entropy of $\Gamma_{\text{SAR}}$ was set at $H_{\Gamma_{\text{SAR}}} = 2.493$.  
It is observed that, for different sample sizes, entropy values converge towards the true value of the Gamma SAR distribution.

```{r Simulated_data_test_gi0_2, echo=FALSE, message=FALSE}

set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(49, 81, 121)
N<- 100
# Number of replications
R <- 100

# Number of bootstrap replications
B <- 2
mu_values <- c(1)
alpha <- -600
L <- 5

  estimators <- list(

    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator
    #"$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
    #"$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
  )
 #true_entropy <- entropy_gamma_sar(L, mu) 
calculate_entropy_and_test_montecarlo <- function(sample_sizes, R, N, B, mu, alpha, L, estimators, true_entropy) {
  true_entropy <- entropy_gamma_sar(L, mu)
  output <- data.frame(
    SampleSize = integer(0),
    Estimator = character(0),
    TypeIErrorRate = numeric(0)
  )

  for (ssize in sample_sizes) {

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      reject_H0_count <- 0

      for (n_replication in 1:N) {

        #samples <- gi0_sample(mu, alpha, L, ssize)
        v.entropy <- numeric(R)
        for (r in 1:R) {

        samples <- gi0_sample(mu, alpha, L, ssize)

        if (grepl(" ", estimator_name)) {
          v.entropy[r] <- estimator(samples, B = B)
        } else {
          v.entropy[r] <- estimator(samples)
        }
      }

        mean_entropy <- mean(v.entropy)
      z_statistic <- sqrt(R) * (mean_entropy - true_entropy) / sd(v.entropy)
      p_value <- 2 * (1 - pnorm(abs(z_statistic)))
      alpha_t = 0.05

        reject_H0_count <- reject_H0_count + sum(p_value < 0.05)
      }

      typeI_error_rate <- reject_H0_count / (N)

      output <- rbind(
        output,
        data.frame(
          SampleSize = ssize,
          Estimator = estimator_name,
          TypeIErrorRate = round(typeI_error_rate, 5)
        )
      )
    }
  }

  colnames(output) <- c("$n$", "Estimator", "Type I Error Rate")

  return(output)
}

calculate_results_test_gi0_montecarlo <- function(sample_sizes, R, N, B, mu_values, alpha, L, estimators) {
  results_list <- list()

    results <- calculate_entropy_and_test_montecarlo(sample_sizes, R, N, B, mu_val, alpha, L, estimators)
    df <- as.data.frame(results)

results_gi0_1_montecarlo <- calculate_results_test_gi0_montecarlo(sample_sizes, R, N, B, mu_values, alpha, L, estimators)
#print(results_gi0_1_montecarlo)
save(results_gi0_1_montecarlo, file = "./Data/results_gi0_1_montecarlo.Rdata")

```{r Table_test_gi0_montecarlo, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
load("./Data/results_gi0_1_montecarlo.Rdata")

for (mu_val in mu_values) {
  results_data <- results_gi0_1_montecarlo[[as.character(mu_val)]]

  table_result <- kbl(
    results_data,
    caption = paste("Type I error with $L=5$, $\\mu=1$ and$\\alpha=\\infty$."),
    format = "latex",
    booktabs = TRUE,
    align = "c",
    escape = FALSE,
    digits = 4,
    label = "table_hipotesis_2"
  ) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")

  #cat("### Results for mu =", mu_val, "\n")
  print(table_result)

}

```
Hypothesis test results were conducted with a \SI{95}{\percent} confidence level. 
The $Z$ statistic measures the discrepancy between the estimated entropy and the true entropy. 
The $p$-values associated with the $Z$ statistic are predominantly greater than $0.05$, for sample sizes above $25$, suggesting that the data are consistent with the null hypothesis.
